Transforming Trash as an Artistic Act

### 2016-01-17 chapter2_reduced.tex
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

@@

% ARTWORK
% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

@@

% ARTWORK
% COFFEE CUP
% FROM http://www.gwynethleech.com/
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
  \caption{Song Dong, Waste Not, 1990}
  \label{fig:SongDong_WasteNot}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
  \caption{Tracey Emin, My Bed, 1998}
  \label{fig:TraceyEmin_MyBed}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/Cesar_Zim.jpg}
  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
  \label{fig:Cesar_Zim}
\end{figure}

@@

>>>>

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Chris Jordan, \textit{Caps Seurat}, 2011, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

@@

% ARTWORK
% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, \textit{Day 169, 363 Days of Tea}, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

@@

% ARTWORK
% COFFEE CUP
% FROM http://www.gwynethleech.com/
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/SongDong_WasteNot.jpg}
  \caption{Song Dong, \textit{Waste Not}, 1990}
  \label{fig:SongDong_WasteNot}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
  \caption{Tracey Emin, \textit{My Bed}, 1998}
  \label{fig:TraceyEmin_MyBed}
\end{figure}

@@

% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor. Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
  \caption{César, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
  \label{fig:Cesar_Zim}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
  \caption{Marcel Duchamp, \textit{Fountain}, 1917, Porcelain urinal}
  \label{fig:Duchamp_Fountaine}
\end{figure}

### 2016-01-17 chapter3_reduced.tex
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/picasso_chair.png}
  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
  \label{fig:Picasso_Chair}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
  \label{fig:Duchamp_BicycleWheel}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell, Found Photos, 1978}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Filomena Cruz, Road Kill, 2014, Photography}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
  \label{fig:Alsbrooks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin, 2014}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
  \caption{Michael Landy, Break Down, 2001}
  \label{fig:MichaelLandy_BreakDown}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/picasso_chair.png}
  \caption{Pablo Picasso, \textit{Still Life with Chair Caning}, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
  \label{fig:Picasso_Chair}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
  \caption{Marcel Duchamp, \textit{Bicycle Wheel}, 1913 (authorised reproduction 1951, original lost)}
  \label{fig:Duchamp_BicycleWheel}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell, \textit{Found Photos}, 1978}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
  \caption{Tim Gaudreau, \textit{Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I}, 2006, Photograph}
  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Filomena Cruz, \textit{Road Kill}, 2014, Photograph}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

@@

% TODO resim yanlış
\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
  \caption{Kim Alsbrooks, \textit{Gen. Jefferson Davis}, 2015, oil on aluminum can}
  \label{fig:Alsbrooks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, \textit{Art Bin}, 2014}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
  \caption{Michael Landy, \textit{Break Down}, 2001}
  \label{fig:MichaelLandy_BreakDown}
\end{figure}
